### 2022-03-03 paper/fse22/intro.tex
change conf name

The prevalent models of NLP are evaluated via train-validation-test
splits. train and validation set is used to train the NLP model and
the \ho set is used for testing by measuring accuracy. The accuracy is
a indicator of the performance of the models.

Despite its usefulness, the main limitation of the testing paradaigm
is that the \ho set often overestimates the performances. Each dataset
comes with specific biases, and the biases increase the discrepancy of
distribution between dataset and
real-world~\cite{recht2019imagenetbias}. The aforementioned accuracy
on \ho set does not consider the discrepancy and it is limited to
achieve comprehensive performrance of the NLP model. As a consequence,
it is difficult to analyze where the errors comes
from~\cite{wu2019errudite}.

On the subject of the limitation of traditional testing paradaigm, a
number of methods have been proposed. First, multiple diagnostic
datasets for evaluating NLP model were introduced for obtaning
generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
that, model is evaluated on different aspects such as robustness of
the model on adversarial
sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial},
fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
consistancy~\cite{ribeiro2019consistencyeval}, prediction
interpretations~\cite{ribeiroSG16lime} and interactive error
analysis~\cite{wu2019errudite}. Especially, \Chlst implements
behavioral testing methodolgy for evaluating multiple linguistic
capabilities of NLP model~\cite{marcoACL2020checklist}. \Chlst
introduces input-output behaviors of linguistic capabilities and
generates behavior-guided inputs for validating the behaviors. It
provides comprehensive behavioral testing of NLP models through a
number of generated inputs. However, the approach only relies on
manually generated input templates, thus the template generation
becomes expensive and time consuming. In addition, the generated
templates are selective and often too simple, and it is limited to
provide restricted evaluation of linguistic capabilities. Thus, it
does not garauntee the comprehensive evaluation.

@@

>>>>

The prevalent models of NLP are evaluated via train-validation-test
splits. train and validation set is used to train the NLP model and
the \ho set is used for testing by measuring accuracy. The accuracy is
a indicator of the performance of the models. Despite its usefulness,
the main limitation of the testing paradigm is that the \ho set often
overestimates the performances. Each dataset comes with specific
biases, and the biases increase the discrepancy of distribution
between dataset and real-world~\cite{recht2019imagenetbias}. The
aforementioned accuracy on \ho set does not consider the discrepancy
and it is limited to achieve comprehensive performrance of the NLP
model. As a consequence, it is difficult to analyze weekness of the
model~\cite{wu2019errudite}.

% this paragraph goes to related, and saying behavioral testing and
% its limitation based on our model's novelty
On the subject of the limitation of traditional testing paradaigm, a
number of methods have been proposed. First, multiple diagnostic
datasets for evaluating NLP model were introduced for obtaning
generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
that, model is evaluated on different aspects such as robustness of
the model on adversarial
sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial},
fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
consistancy~\cite{ribeiro2019consistencyeval}, prediction
interpretations~\cite{ribeiroSG16lime} and interactive error
analysis~\cite{wu2019errudite}. Especially, \Chlst implements
behavioral testing methodolgy for evaluating multiple linguistic
capabilities of NLP model~\cite{marcoACL2020checklist}. \Chlst
introduces input-output behaviors of linguistic capabilities and
generates behavior-guided inputs for validating the behaviors. It
provides comprehensive behavioral testing of NLP models through a
number of generated inputs. However, the approach only relies on
manually generated input templates, thus the template generation
becomes expensive and time consuming. In addition, the generated
templates are selective and often too simple, and it is limited to
provide restricted evaluation of linguistic capabilities. Thus, it
does not garauntee the comprehensive evaluation.

@@

% our paper's contribution
